Stack Safety as a Security Property

### 2020-07-09 main.tex
Clean up blessed sequences

To enforce this discipline, we define blessed header and return instruction
sequences. These are specific sequences of tagged instructions that are intended
to appear at the beginning and end of each function:

\[
  \begin{array}{c|c|c}
    {\sw ~ \rsp ~ \rra ~ 1} & {\tagHa, \tagInstr} & \text{Store RA in stack} \\
    {\addi ~ \rsp ~ \rsp ~ 2} & {\tagHb, \tagInstr} & \text{Increment SP by frame size}
  \end{array}
  \]

\[
  \begin{array}{c|c|c}
    {\lw ~ \rra ~ \rsp ~ -1} & {\tagRa, \tagInstr} & \text{Load RA} \\
    {\addi ~ \rsp ~ \rsp ~ -2} & {\tagRb, \tagInstr} & \text{Decrement SP by frame size} \\
    {\jalr ~ \rra ~ \rra} & {\tagRc, \tagInstr} & \text{Jump back}
  \end{array}
\]

>>>>

To enforce this discipline, we define blessed header and return instruction
sequences. These are specific sequences of tagged instructions that are intended
to appear at the beginning and end of each function. This is the header
sequence:
%
\setcounter{pcctr}{1}
\[
  \begin{array}{l|l|l|l}
     & \mathit{Instruction} & \mathit{Tags} & \\
    \hline
    \row{\sw ~ \rsp ~ \tta ~ 1}{[\rsp+1] \leftarrow \rra}{\tagHa, \tagInstr}
        {Store return address in stack}
    \row{\addi ~ \rsp ~ \rsp ~ 2}{\rsp \leftarrow \rsp + 2}{\tagHb, \tagInstr}
        {Increment stack pointer by frame size}
  \end{array}
\]
%
And the return sequence:
%
\setcounter{pcctr}{1}
\[
  \begin{array}{l|l|l|l}
     & \mathit{Instruction} & \mathit{Tags} & \\
    \hline
    \row{\lw ~ \rra ~ \rsp ~ \negate 1}{\rra \leftarrow [\rsp - 1]}{\tagRa, \tagInstr}
        {Load return address}
    \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\tagRb, \tagInstr}
        {Decrement stack pointer by frame size}
    \row{\jalr ~ \rra ~ \rra ~ 0\apt{wrong}}{\PCname \leftarrow \rra}{\tagRc, \tagInstr}
        {Return to caller ($\jalr$)}
  \end{array}
\]
